\documentclass[10pt,a4paper,ragged2e,withhyper]{files/altacv}
% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.25cm}
\usepackage{paracol}
\usepackage{marvosym}
\usepackage[backend=biber,style=ieee,sorting=ydnt,defernumbers=true]{biblatex}
% Font selection for pdflatex
\usepackage[rm]{roboto}
\usepackage[defaultsans]{lato}
\renewcommand{\familydefault}{\sfdefault}

% Original colors
\definecolor{primary}{RGB}{0,76,153}
\definecolor{secondary}{RGB}{50,50,50}
\colorlet{name}{black}
\colorlet{tagline}{primary}
\colorlet{heading}{primary}
\colorlet{headingrule}{primary}
\colorlet{subheading}{secondary}
\colorlet{accent}{primary}
\colorlet{emphasis}{secondary}
\colorlet{body}{secondary}

% Font and formatting settings
\renewcommand{\namefont}{\Large\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize\textit}
\renewcommand{\cvsectionfont}{\large\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}

\begin{document}

\name{Md. Shakibul Islam}
\tagline{\normalsize{Computer Engineer | Graphic Designer}}
\vspace{4mm}
\personalinfo{
    \email{shakibulislammobin@gmail.com}
    \phone{+8801746 301800}
    \github{siMobin}
    \linkedin{md-shakibul-islam-858467272}
    \printinfo{\faMapMarker}{Dhaka, Bangladesh}
}
\makecvheader
\divider
\columnratio{0.6}

\begin{paracol}{2}

    % Work Experience
    \cvsection{Work Experience}
    \cvevent{Intern IT Executive}{Youth For Bangladesh \hfill October 2024 -- Present}{}{}
    \begin{itemize}
        \item Web application development and feature implementation.
        \item Maintaining and updating existing web applications.
        \item Managing IT systems and providing technical support.
        \item Drafting official documents and organizational content.
        \item Graphic design using Adobe Illustrator and Photoshop.
        \item Video editing for promotional and social media content.
        \item Capturing and managing photo and video content during organizational events.
    \end{itemize}

    \divider

    \cvevent{Full Stack Web Developer}{Self-employed \hfill 2023 -- Present}{}{}
    \begin{itemize}
        \item Designed and developed full-stack web applications.
        \item Built responsive, user-friendly interfaces following modern UI/UX.
        \item Implemented backend logic, APIs, authentication, and database management for real-world client projects.
        \item Managed end-to-end project lifecycle including requirement analysis, development, deployment, and maintenance.
        \item Communicated directly with clients to gather requirements, provide updates, and ensure satisfaction.
    \end{itemize}
    \vspace{4mm}

    % Switch to right column
    \switchcolumn

    % Skills
    \cvsection{Skills}
    \newcommand{\skilltag}[2]{\textbf{#1:} #2}

    \skilltag{Frontend}{Next.js, React, TypeScript, Vite, HTML, CSS, SCSS, Tailwind CSS}\\[0.5em]
    \skilltag{Backend}{PHP, Laravel, Filament, Node.js}\\[0.5em]
    \skilltag{Programming Languages}{JavaScript, TypeScript, PHP, Python, Java, C++, C}\\[0.5em]
    \skilltag{Database}{Microsoft SQL Server, MySQL, PostgreSQL, SQLite}\\[0.5em]
    \skilltag{DevOps \& Deployment}{Git, GitHub, Docker, CI/CD (GitHub Actions), Vercel, Cloudflare}\\[0.5em]
    \skilltag{Design Tools}{Photoshop, Illustrator, Adobe XD, Premiere Pro}\\[0.5em]
    \skilltag{Operating Systems}{Windows, Linux (Ubuntu)}\\[0.5em]

    \vspace{4mm}

    % Education
    \cvsection{Education}
    \cvevent{B.Sc. in Computer Science and Engineering}{Stamford University Bangladesh}{}{}
    \begin{itemize}[leftmargin=0cm, label={\color{primary}}, itemsep=0pt]
        \item  \faGraduationCap\ Graduated: 2025 \hspace{3mm} \faMedal\ CGPA: 3.20/4.00
    \end{itemize}

    % Certifications
    \cvsection{Certifications}
    \cvachievement{\faCertificate}{Digital Marketing}{Future IT \& Language Training Institute, 2023}\\[0.5em]
    \cvachievement{\faCertificate}{AI \& Machine Learning Boot Camp}{EATL Innovation Hub, Feb 2025}
    \vspace{4mm}

    % % Languages
    % \cvsection{Languages}
    % % \bfseries Bengali: Native \hfill English: Fluent
    % \begin{itemize}[leftmargin=0cm, label={\color{primary}}, itemsep=0pt]
    %     \item \textbf{Bengali}: Native \hspace{0.5cm} \textbf{English}: Fluent
    % \end{itemize}

\end{paracol}

\cvsection{Projects}

% Left Column
\columnratio{0.5}
\begin{paracol}{2}
    \cvevent{Flicker Engineering \hfill \footnotesize\textit{Next.js}}{}{}{}
    \small \faChevronRight \ Corporate website for industrial engineering services. Providing a professional digital presence. \\[0.5em]
    \small \faGlobe \ \href{https://www.flickerengineering.com}{www.flickerengineering.com}

    \divider

    \cvevent{Help The Children Foundation \hfill \footnotesize\textit{Next.js}}{}{}{}
    \small \faChevronRight \ Official website for Help The Children Foundation. \\[0.5em]
    \small \faGlobe \ \href{https://hcfbd.org}{hcfbd.org}

    \divider

    \cvevent{HCF Admin Panel \hfill \footnotesize\textit{PHP, Laravel, Filament}}{}{}{}
    \small \faChevronRight \ Daily 10 School Student and Sponsor Control system with Filament dashboard, Cloudinary assets, and API support. \\[0.5em]
    \small \faGlobe \ \href{https://admin.hcfbd.org}{admin.hcfbd.org}

    \divider

    \cvevent{Youth For Bangladesh \hfill \footnotesize\textit{Next.js}}{}{}{}
    \small \faChevronRight \ Official website for Youth For Bangladesh. \\[0.5em]
    \small \faGlobe \ \href{https://youthforbangladesh.org}{youthforbangladesh.org}

    \divider

    \cvevent{Boishakhi Trade Int. \hfill \footnotesize\textit{Next.js}}{}{}{}
    \small \faChevronRight \ International education consultancy and student support platform empowering global study opportunities. \\[0.5em]
    \small \faGlobe \ \href{https://www.boishakhitradeint.com}{www.boishakhitradeint.com}

    \divider

    \cvevent{Point of Sales \hfill \footnotesize\textit{PHP, Laravel, Livewire}}{}{}{}
    \small \faChevronRight \ A web-based application that provides a comprehensive solution for managing inventory, sales, and expenses for businesses with multiple branches.

    \divider

    \cvevent{Airline Management System \hfill \footnotesize\textit{PHP, SCSS, MSSQL}}{}{}{}
    \small \faChevronRight \ Private jet hiring and airline management system featuring flight scheduling, reservations, and role-based admin user workflows. \\[0.5em]
    \small \faGithub \ \href{https://github.com/siMobin/airline-reservation-system}{github.com/siMobin/airline-reservation-system}

    % \divider
    % Right Column
    \switchcolumn

    \cvevent{YFBD Donation System \hfill \footnotesize\textit{Vite, React, TS}}{}{}{}
    \small \faChevronRight \ Payment and contribution platform for YFBD using bKash payment gateway. \\[0.5em]
    \small \faGlobe \ \href{https://donate.yfbd.org/}{donate.yfbd.org}

    \divider

    \cvevent{Youth News \hfill \footnotesize\textit{Next.js}}{}{}{}
    \small \faChevronRight \ Comprehensive news portal delivering real-time updates with modern SEO optimization. \\[0.5em]
    \small \faGlobe \ \href{https://youthnewsbd.com}{youthnewsbd.com}

    \divider

    \cvevent{Youth News Admin Panel \hfill \footnotesize\textit{Vite}}{}{}{}
    \small \faChevronRight \ Powerful administrative interface for managing news content, users, and advertising. \\[0.5em]
    \small \faGlobe \ \href{https://admin.youthnewsbd.com}{admin.youthnewsbd.com}

    \divider

    \cvevent{Gemini Echo \hfill \footnotesize\textit{Vite, TypeScript}}{}{}{}
    \small \faChevronRight \ A conversational AI that interacts with users as a \faVenus partner (system\_instructions). Ability to processes text, images, videos, audio, and documents, with memory capabilities to retain and recall information. \\[0.5em]
    \small \faGithub \ \href{https://github.com/siMobin/Gemini-Echo\_TS}{github.com/siMobin/Gemini-Echo\_TS}

    \divider

    \cvevent{Super Mario Runner \hfill \footnotesize\textit{Java}}{}{}{}
    \small \faChevronRight \ This Java-based recreation seamlessly blends the timeless charm of the Chrome Dino game with the vibrant world of Super Mario Bros. \\[0.5em]
    \small \faGithub \ \href{https://github.com/siMobin/superMarioRunner}{github.com/siMobin/superMarioRunner}

    \divider

    \cvevent{Student Management System \hfill \footnotesize\textit{.NET, MSSQL}}{}{}{}
    \small \faChevronRight \ A CLI application for handling simple CRUD operations on a student database. \\[0.5em]
    \small \faGithub \ \href{https://github.com/siMobin/StudentManagementSystem}{github.com/siMobin/StudentManagementSystem}

\end{paracol}

\vspace{4mm}
\centering \faFire \textit{Explore more at \href{https://github.com/siMobin/}{github.com/siMobin}.}\faFire

\end{document}
