\cvsection{Projects}

% Left Column
\columnratio{0.5}
\begin{paracol}{2}
    \cvevent{Flicker Engineering \hfill \footnotesize\textit{Next.js}}{}{}{}
    \small \faChevronRight \ Corporate website for industrial engineering services. Providing a professional digital presence. \\[0.5em]
    \small \faGlobe \ \href{https://www.flickerengineering.com}{www.flickerengineering.com}

    \divider

    \cvevent{Help The Children Foundation \hfill \footnotesize\textit{Next.js}}{}{}{}
    \small \faChevronRight \ Official website for Help The Children Foundation. \\[0.5em]
    \small \faGlobe \ \href{https://hcfbd.org}{hcfbd.org}

    \divider

    \cvevent{HCF Admin Panel \hfill \footnotesize\textit{PHP, Laravel, Filament}}{}{}{}
    \small \faChevronRight \ Daily 10 School Student and Sponsor Control system with Filament dashboard, Cloudinary assets, and API support. \\[0.5em]
    \small \faGlobe \ \href{https://admin.hcfbd.org}{admin.hcfbd.org}

    \divider

    \cvevent{Youth For Bangladesh \hfill \footnotesize\textit{Next.js}}{}{}{}
    \small \faChevronRight \ Official website for Youth For Bangladesh. \\[0.5em]
    \small \faGlobe \ \href{https://youthforbangladesh.org}{youthforbangladesh.org}

    \divider

    \cvevent{Boishakhi Trade Int. \hfill \footnotesize\textit{Next.js}}{}{}{}
    \small \faChevronRight \ International education consultancy and student support platform empowering global study opportunities. \\[0.5em]
    \small \faGlobe \ \href{https://www.boishakhitradeint.com}{www.boishakhitradeint.com}

    \divider

    \cvevent{Point of Sales \hfill \footnotesize\textit{PHP, Laravel, Livewire}}{}{}{}
    \small \faChevronRight \ A web-based application that provides a comprehensive solution for managing inventory, sales, and expenses for businesses with multiple branches.

    \divider

    \cvevent{Airline Management System \hfill \footnotesize\textit{PHP, SCSS, MSSQL}}{}{}{}
    \small \faChevronRight \ Private jet hiring and airline management system featuring flight scheduling, reservations, and role-based admin user workflows. \\[0.5em]
    \small \faGithub \ \href{https://github.com/siMobin/airline-reservation-system}{github.com/siMobin/airline-reservation-system}

    % \divider
    % Right Column
    \switchcolumn

    \cvevent{YFBD Donation System \hfill \footnotesize\textit{Vite, React, TS}}{}{}{}
    \small \faChevronRight \ Payment and contribution platform for YFBD using bKash payment gateway. \\[0.5em]
    \small \faGlobe \ \href{https://donate.yfbd.org/}{donate.yfbd.org}

    \divider

    \cvevent{Youth News \hfill \footnotesize\textit{Next.js}}{}{}{}
    \small \faChevronRight \ Comprehensive news portal delivering real-time updates with modern SEO optimization. \\[0.5em]
    \small \faGlobe \ \href{https://youthnewsbd.com}{youthnewsbd.com}

    \divider

    \cvevent{Youth News Admin Panel \hfill \footnotesize\textit{Vite}}{}{}{}
    \small \faChevronRight \ Powerful administrative interface for managing news content, users, and advertising. \\[0.5em]
    \small \faGlobe \ \href{https://admin.youthnewsbd.com}{admin.youthnewsbd.com}

    \divider

    \cvevent{G-Max Group BD. \hfill \footnotesize\textit{Next.js}}{}{}{}
    \small \faChevronRight \ G-Max Group is a diversified company specializing in agriculture, events, and international trade. \\[0.5em]
    \small \faGlobe \ \href{https://gmaxgroupbd.com/}{gmaxgroupbd.com}

    \divider

    \cvevent{Gemini Echo \hfill \footnotesize\textit{Vite, TypeScript}}{}{}{}
    \small \faChevronRight \ A conversational AI that interacts with users as a \faVenus partner (system\_instructions). Ability to processes text, images, videos, audio, and documents, with memory capabilities to retain and recall information. \\[0.5em]
    \small \faGithub \ \href{https://github.com/siMobin/Gemini-Echo\_TS}{github.com/siMobin/Gemini-Echo\_TS}

    \divider

    \cvevent{Super Mario Runner \hfill \footnotesize\textit{Java}}{}{}{}
    \small \faChevronRight \ This Java-based recreation seamlessly blends the timeless charm of the Chrome Dino game with the vibrant world of Super Mario Bros. \\[0.5em]
    \small \faGithub \ \href{https://github.com/siMobin/superMarioRunner}{github.com/siMobin/superMarioRunner}

    \divider

    \cvevent{Student Management System \hfill \footnotesize\textit{.NET, MSSQL}}{}{}{}
    \small \faChevronRight \ A CLI application for handling simple CRUD operations on a student database. \\[0.5em]
    \small \faGithub \ \href{https://github.com/siMobin/StudentManagementSystem}{github.com/siMobin/StudentManagementSystem}

\end{paracol}

% Space and Footer
\vspace{4mm}
\centering \faFire \textit{Explore more at \href{https://github.com/siMobin/}{github.com/siMobin}.}\faFire